Behavior Driven Development in Haskell

### 2012-05-24 paper.tex
Introduction: wording
Remove trailing whitespace
Describe hspec

@@

\begin{quote}
    \emph{Would we need evidence to support the claim that "Haskell programs have less bugs"?}
\end{quote}

Unfortunately, the strong type system of Haskell does not guarantee correct
semantic.
Haskellers is, however, apt to rely on the strong type system too much.
They tend to write less test code than programmers of other
programming languages.

@@

TBD(@sol): talk about hspec.

\begin{quote}
\small
\begin{verbatim}
TBD: Example
\end{verbatim}
\end{quote}

>>>>

\newcommand{\hspec}{Hspec}

@@

Unfortunately, the strong type system of Haskell does not guarantee correct
semantic.

\begin{quote}
    \emph{TBD: What about dependent types and GHC's new features?}
\end{quote}

Haskell programmers, however, tend to rely on the type system too much.  They
tend to write less test code than programmers of other programming languages.

@@

If we have some behavior that does not fit into the user documentation, but
would rather be part of a design document, we use \hspec{}.

\hspec{} provides an EDSL for defining specs.  A spec organizes behavior in a
tree structure, and it is defined with \texttt{it} and \texttt{describe}.

\begin{quote}
\small
\begin{verbatim}
spec :: Specs
spec = do
  describe "reverse" $ do
    it "reverses a list" $
      reverse [1 :: Int, 2, 3] @?= [3, 2, 1]

    it "gives the original list, if applied twice" $ property $
      \xs -> reverse (reverse xs) == (xs :: [Int])
\end{verbatim}
\end{quote}

\noindent The {\tt it} function combines a text description for a behavior and
a property or an example that gives some confidence in that behavior into a
spec.
Examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties inot a \texttt{Property}.

The \texttt{describe} function combines a list of specs into a larger spec.  It
can be used to organize a spec as a tree.
Internally, a \texttt{Writer} is used to build up specs in a monadic way.

A spec can be run with the \texttt{hspecX} function.  When a spec is run, all
properties and examples are evaluated, and failing properties and examples are
reported to the user (FIXME: user does not fit our definition of \emph{user}
here!).
